### 2016-03-15 paper/result_optical_flow.tex
Hang
ref

% 
% This is because some solution proposals are more effective than others,
% so once a thread grabs an effective solution proposal, it find a lower
% energy quickly. Since there is no solution sharing in PFM model, other
% threads cannot share this lower energy state, and keeps working on its
% own state.
%
%On the other hand, SF-MF
%allows solution sharing, so once a thread grabs an effective solution
%proposal and moves to a lower energy state, other threads can share
%information about this lower energy state. In this manner, all threads
%contribute to further decrease of this low energy state. To further
%demonstrate what is happening here,
To further investigate the effectiveness of solution sharing,
Figure~\ref{fig:optical_flow_by_threads} shows the energy plots of PFM
and SF-MF per thread. As evident from the plot, in PFM, threads need to
keep working independently at higher energy states.
%in PFM, one thread found a better solution than others, but other
%threads keep working independently at higher energy states.
SF-MF, on the other hand, exchanges solutions all the time, and every
thread is making an effective work in improving the solution.
%As we can see from the plots, in PFM model, one thread finds lower
%energy state faster than others, while other threads keep working at
%their own energy state. But in SF-MF model, all threads exchange
%information about the lowest energy state frequently and work on
%improving the lowest energy state together. Since the solution for
%optical flow can be locally improved by each thread, the final merging
%of PFM can effectively fuse good local results in different threads
%together and achieve a similar energy state with SF-MF model. But as
%SF-MF model shares information in the middle, a final merging becomes
%less necessary.
Another key finding from Fig.~\ref{fig:optical_flow_convergence} is that
SF is slower than SF-MF. Our analysis is that multi-way fusion is
inefficient in this problem setting, since solution proposals are
relatively independent and fusing the solution space would not gain much
benefit. It rather loses performance against QPBO~\cite{QPBO} due to the
overhead of TRW-S.

There are two factors influencing solution sharing: 1) \textit{the
number of solutions to share} and 2) \textit{the frequency of solution
sharing}. Both factors are controlled by $\beta$. As mentioned in
Section~\ref{section:algorithm}, we have used $\beta = 1$ (i.e., share
solutions) once in every five iterations.  To further understand the
effects of solution sharing, we conducted two more experiments. First,
we set $\beta$ to 0, 1, 2, or 3 in every five iterations,
% (when $\beta = 0$, it is the same with PFM without final merging).
while keeping all other parameters the same (See
Fig.~\ref{fig:opticalflow_configuration}(left)).  Second, we change the number of
iterations $k$ between the two consecutive solution sharing iterations
(See Fig.~\ref{fig:opticalflow_configuration}(right)).  The first experiment
revealed that the solution sharing makes convergence faster regardless of
$\beta$.  However, too much solution sharing slows down the convergence,
and $\beta=1$ is the sweet spot for this problem.
%
% , energy generally
% decreases faster with solution sharing. But since we need to perform one
% fusion for sharing each solution, sharing more solution decreases
% efficiency in this problem setting. While sharing multiple solutions
% might be useful in some other problem setting as it means each thread
% can get more global information early.
%
The second experiment has shown that too frequent solution sharing
harms the convergence, simply because threads have less time generating more
proposals and exploring the solution space.
% From this figure, we can see that
% although solution sharing generally speeds up the optimization process,
% sharing solution too frequently is not a good practice. This is because
% when we share solution frequently, we have less time for generating and
%fusing new proposals.
Optimal parameter setting depends on each problem setting.
%A good choice of the solution sharing frequency depends on specific
%problem setting.

>>>>

% 
% This is because some solution proposals are more effective than others,
% so once a thread grabs an effective solution proposal, it find a lower
% energy quickly. Since there is no solution sharing in PFM model, other
% threads cannot share this lower energy state, and keeps working on its
% own state.
%
%On the other hand, SF-MF
%allows solution sharing, so once a thread grabs an effective solution
%proposal and moves to a lower energy state, other threads can share
%information about this lower energy state. In this manner, all threads
%contribute to further decrease of this low energy state. To further
%demonstrate what is happening here,
To further investigate the effectiveness of solution sharing,
Figure~\ref{fig:optical_flow_by_threads} shows the energy plots of PFM
and SF-MF per thread. As evident from the plot, in PFM, threads need to
keep working independently at higher energy states.
%in PFM, one thread found a better solution than others, but other
%threads keep working independently at higher energy states.
SF-MF, on the other hand, exchanges solutions all the time, and every
thread is making an effective work in improving the solution.
%As we can see from the plots, in PFM model, one thread finds lower
%energy state faster than others, while other threads keep working at
%their own energy state. But in SF-MF model, all threads exchange
%information about the lowest energy state frequently and work on
%improving the lowest energy state together. Since the solution for
%optical flow can be locally improved by each thread, the final merging
%of PFM can effectively fuse good local results in different threads
%together and achieve a similar energy state with SF-MF model. But as
%SF-MF model shares information in the middle, a final merging becomes
%less necessary.
Another key finding from Fig.~\ref{fig:optical_flow_convergence} is that
SF is slower than SF-MF. Our analysis is that multi-way fusion is
inefficient in this problem setting, since solution proposals are
relatively independent and fusing the solution space would not gain much
benefit. It rather loses performance against QPBO due to the
overhead of TRW-S.

There are two factors influencing solution sharing: 1) \textit{the
number of solutions to share} and 2) \textit{the frequency of solution
sharing}. Both factors are controlled by $\beta$. As mentioned in
Section~\ref{section:optical_flow}, we have used $\beta = 1$ (i.e., share
solutions) once in every five iterations.  To further understand the
effects of solution sharing, we conducted two more experiments. First,
we set $\beta$ to 0, 1, 2, or 3 in every five iterations,
% (when $\beta = 0$, it is the same with PFM without final merging).
while keeping all other parameters the same (See
Fig.~\ref{fig:opticalflow_configuration}(left)).  Second, we change the number of
iterations $k$ between the two consecutive solution sharing iterations
(See Fig.~\ref{fig:opticalflow_configuration}(right)).  The first experiment
revealed that the solution sharing makes convergence faster regardless of
$\beta$.  However, too much solution sharing slows down the convergence,
and $\beta=1$ is the sweet spot for this problem.
%
% , energy generally
% decreases faster with solution sharing. But since we need to perform one
% fusion for sharing each solution, sharing more solution decreases
% efficiency in this problem setting. While sharing multiple solutions
% might be useful in some other problem setting as it means each thread
% can get more global information early.
%
The second experiment has shown that too frequent solution sharing
harms the convergence, simply because threads have less time generating more
proposals and exploring the solution space.
% From this figure, we can see that
% although solution sharing generally speeds up the optimization process,
% sharing solution too frequently is not a good practice. This is because
% when we share solution frequently, we have less time for generating and
%fusing new proposals.
Optimal parameter setting depends on each problem setting.
%A good choice of the solution sharing frequency depends on specific
%problem setting.
